---
title: "Lab 2"
author: "Cesar Nillaga"
date: "4/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
library(dplyr)
library(cowplot)
library(colorspace)
library(ggrepel)
```


### Dissecting a Bad Visualization

1. While there are certainly issues with this image, do your best to tell the story of this graph in words. That is, what is this graph telling you? What do you think the authors meant to convey with it?

The graph is showing the distribution of the world countries and they're beliefs on whether the vaccine is safe or not. The dark lines in the distribution show the median for each region group in the world. It would appear that the authors are trying to show the differences between countries in a region and then the overall difference between regions. 

2. List the variables that appear to be displayed in this visualization.

+ Region
+ Country 
+ Belief Percentage 

3. Now that you're versed in the grammar of graphics (ggplot), list the aesthetics used and which variables are specified for each.

+ frontface; region 
+ color; region 

4. What type of graph would you call this?

+ line chart or scatterplot 

5. List all of the problems or things you would improve about this graph.  

+ The scale is misleading, Former Soviet Union and Asia have some values in which people who believe vaccines are safe and its look as if Asia is higher than the other country. 
+ The extra points that are labeled may not be necessary if they are just trying to compare the larger countries of the world. 


### Improving the Bad Visualization


```{r, echo = FALSE}
countries <- read_excel("wgm2018-dataset-crosstabs-all-countries.xlsx", sheet = "Full dataset")   # reading in dataset 
```


```{r, echo = FALSE}
# from the dataset anything greater than three iS considered as yes 
percent_yes <- function(question){
  if_else(question >= 3, 1, 0, missing = NULL)         
}
```




```{r, echo=FALSE}
countries <- countries %>%
  group_by(WP5) %>%
  mutate(total = percent_yes(Q25),                            
         percent = (sum(total, na.rm = TRUE) / length(WP5)) * 100,        # creating percentage based on countries "beliefs"
         regions = case_when(
           Regions_Report == 1 ~ 'Africa',
           Regions_Report == 2 ~ 'Africa',
           Regions_Report == 4 ~ 'Africa',
           Regions_Report == 5 ~ 'Africa',
           Regions_Report == 18 ~ 'Africa',                      # creating a regions variable that combines all regions into one 
           Regions_Report == 3 ~ 'Middle East',
           Regions_Report == 14 ~ 'Middle East',
           Regions_Report == 6 ~ 'Americas',
           Regions_Report == 7 ~ 'Americas',
           Regions_Report == 8 ~ 'Americas',
           Regions_Report == 14 ~ 'Europe',
           Regions_Report == 15 ~ 'Europe',
           Regions_Report == 16 ~ 'Europe',
           Regions_Report == 17 ~ 'Europe',
           Regions_Report == 9 ~ 'Asia',
           Regions_Report == 10 ~ 'Asia',
           Regions_Report == 11 ~ 'Asia',
           Regions_Report == 12 ~ 'Asia',
           TRUE ~ 'NA'
         ))              
```




```{r, echo=FALSE}
countries %>%
  ggplot(aes(x = WP5, y = percent, group = WP5, label = WP5)) +         # grouping by country
  geom_point(aes(color = WBI, fill = WBI),                              # filling by world income level
               size = 2.5, alpha = 0.5,
               shape = 21) +
  facet_wrap(~ regions) +                                               # creating separate plots based on region
  xlab("Countries") +
  ylab("Percent who Believe Vaccines are Safe") +
  ggtitle("Percent of People who believe Vaccines are Safe By Country and Global Region") +
  geom_text(data = subset(countries, percent > 50)) +                 # labeling countries with percent higher than 50
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_classic() 
```



## Part Two: Broad Visualization Improvement (200 points)


### Second Data Visualization Improvement

1. Page 66 Chart 3.8. The others here are trying to show relationship between the countries life expectancy and people who trust the doctors and nurses. The others are really just trying to show the differences between countries but I believe there can be something improved about this graph that wasn't factored in. 
2. 
+ Countries Life Expectancy 
+ Trust for nurses or doctors

3. aes(x = Life Expectancy, y = Trust for nurses or doctors)

4. Scatterplot

5. I feel the only problem is the graph doesn't tell the whole story. Some countries have different income levels so this can be huge factor in life expectancy and this can also be related to trust in nurses and doctors. If there isnt enough money for the healthcare workers people may not have a large amount of trust in them. 

6. 

```{r, echo=FALSE}
percent_yes <- function(question){
  if_else(question <= 2, 1, 0, missing = NULL)                    # change values based on survey questions
}

countries <- countries %>%                                        # creating new variable based on nurses survey
  group_by(WP5) %>%
  mutate(total1 = percent_yes(Q22),
         percent_nurse = (sum(total1, na.rm = TRUE) / length(WP5)) * 100,
         life_exp = mean(Age, na.rm = TRUE))      
```




```{r, echo=FALSE}
countries %>%
  ggplot(aes(life_exp, percent_nurse)) +
    geom_point(aes(color = WBI, fill = WBI),
               size = 2.5, alpha = 0.5,
               shape = 21) +
  xlab("Average Life Expectancy") +
  ylab("Percentage who have trust in doctors/nurses") +
  theme_classic() 
```

